The influence of resource use on yield versus sale price trade-off in Australian vineyards

### 2024-05-28 article.tex
Fixed Figures for PLOS One Submission

The focus on sustainability in agronomic industries has changed the way in which these enterprises do business. The diverse nature of vineyard operations results in complicated interactions with both environmental and economic outcomes. The interactions between different factors can put an environmentally advantageous decision at odds with an economic one, and conversely economic decisions can be detrimental to the environment \cite{beaumelleBiodiversityConservationEcosystem2023}. As a result many studies are including more diverse ranges of data and scales. However, studies tend to focus on specific aspects, such as reducing chemical use or improving soil health, often focusing on singular relationships or variable outcomes \cite{barriguinhaVineyardYieldEstimation2021,heFruitYieldPrediction2022,laurentReviewIssuesMethods2021}. Other analyses, look at life cycles or cost benefit analyses, reflecting a specific management decision's outcome \cite{abbottAWRIAssessingEnvironmental2016,beauchetInterannualVariabilityEnvironmental2019,ferraraLifeCycleAssessment2018} or their cost benefits by utilising different scenarios to assess specific practices \cite{fincoCombiningPrecisionViticulture2022a,singhBibliometricReviewUse2022}. It has been noted that some studies have relied too heavily on single points of engagement when relaying the idea of sustainability and vineyard outcomes, especially when the inclusion of more variables or data could have better described a situation as a whole \cite{baianoOverviewSustainabilityWine2021,santiago-brownSustainabilityAssessmentWineGrape2015}. The changing nature of sustainability also calls for measures to be more than simple snapshots of data \cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023,santiago-brownSustainabilityAssessmentWineGrape2015}. Given recent studies there is still growing interest from the winegrowing industry in further studies, with several recent reviews calling for more research to demonstrate the potential trade-offs between different operational approaches across different climates and regions \cite{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.

A dilemma exists across agriculture through shared fundamental considerations of resource use such as water and fuel, and the resultant yield and crop value that are produced \cite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. The average price of grapes for wine production is driven through its integration within the wine industry. An important connection between grapes and their price is the grape's perceived quality, which initially defines a wine's potential through the grape's chemical makeup \cite{blackTerpenoidsTheirRole2015,schreierFlavorCompositionWines1979}. Grapes of higher perceived quality or grapes from well known regions are likely to have higher prices \cite{wineaustraliaNationalVintageReport2021}.  Grape quality is connected to the market value of winegrapes, with Wine Australia explicitly defining grape quality through the use of discrete price brackets in their annual reports \cite{winemakersfederationofaustraliaNationalVintageReport2018}. It is important to note that the generalisation made to reflect quality through using average price assumes a due diligence of those who purchase the grapes \cite{yeggeInfluenceSensoryNonsensory2001}. The economic sustainability of a vineyard is tied to this market culture, driven by the wine industry. The consideration of sustainability within viticulture is also subject to environmental and sociodemographic pressures \cite{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these pressures include biosecurity, climate and international market changes \cite{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the varied effects of factors on grape quality and yield \cite{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. Due to the lack of long-term and in-depth data there is a lack of research on grape sale price and its driving factors. Furthermore, individual factors are often studied in isolation with yield and sales price not appearing together \cite{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions. As a result, broader studies are lacking \cite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and average sale price of the resultant product, taking into account the size and location of the vineyard. In a practical sense, this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the trade-off between invested resources, yield and average sale price. This is the first time that such a trade-off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section*{Methods}
\subsection*{Data}

@@

Data used in these analyses were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape  growers and winemakers in demonstrating and improving their sustainability \cite{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act \cite{attorney-generalsdepartmentWineAustraliaCorporation2010}. Data collected by Wine Australia are publicly available. The response (predicted) variables in this analysis were yield, defined as the total tonnes of grapes harvested, and average sale price of grapes in Australian dollars per tonne. Both response variables were examined as totals and also relative to area harvested (see Table \ref{tab:tab1}). Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

Data recorded by Sustainable Winegrowing Australia were entered manually by winegrowers voluntarily using a web based interface. For each model, vineyards were only included if they recorded all the variables used for the corresponding model (see Table \ref{tab:tab1}). Each vineyard had at least recorded region, harvest year, yield and area harvested. Other variables that were used but not present for every single vineyard were average sale price, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable direct comparisons between fuels, fuel use was converted to tonnes of carbon dioxide equivalent and collectively referenced to as emissions. All variables were continuous except for harvest year and region, which were categorical variables (Table \ref{tab:tab1}).

@@

The dataset was split into two distinct subsets that could be used across the different models. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table \ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for three further models (Models 3, 4 and 5, see Table \ref{tab:tab1}). These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table \ref{tab:tab1}), as every sample/vineyard had a recorded value for yield but not average price of sale per tonne.

@@

The first subset of data (used for Model 1 and Model 2, see Table \ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 discrete vineyards.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table \ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards. Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

Data preprocessing was conducted prior to analysis using the Python programming language \cite{g.vanrossumPythonTutorialTechnical1995}. Preprocessing included the conversion of fuel to scope one emissions and prior calculations for all continuous variables which included logarithmic transformations, centring and scaling by standard deviation. 
We converted multiple emission sources into scope one emissions using the equation given from the Australian National Greenhouse Accounts Factors \cite{agdeeNationalGreenhouseAccounts2021}. The calculation conducted using

@@

where emissions was the the product of the quantity of fuel in litres, $Q$, a prescribed Energy Content, $EC$, and emission factors (as given by the Australian National Greenhouse Accounts factors) of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide Emission equivalent, $tCO2e$ \cite{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}

@@

Differences in vineyard locations were captured through the use of Geographical Indicator Regions defined by Wine Australia \cite{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Although vineyards generally differed in income, there were pronounced differences between regions as shown in Figure \ref{fig:map}. These differences were likely due to the site of a vineyard being important as it predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and average sale price \cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act \cite{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

 The climatic properties of each GI Region were summarised by using predefined classifications as per the \cite{sustainablewinegrowingaustraliaSustainableWinegrowingAustralia2021} user manual. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI Regions.

@@

Five general linear models (GLMs) were created (see Table \ref{tab:tab1}). GLMs were chosen as they offer the ability to produce statistical models that are explicit in the relationships between predictors and response variables.  General Linear Models also allowed the exploration of interactions between predictors and allow for easily comparable differences in the influence and magnitude of relationships. Model fit was measured in terms of $R^2$ and adjusted $R^2$ as well as F statistics, and t-tests were used to determine if predictors significantly contributed to the models when accounting for other variables, showing which specific years and areas contributed significantly. Both the PPCC and GLM analyses were created using the R statistical programming language \cite{rcoreteamLanguageEnvironmentStatistical2021} with the Caret package \cite{kuhnBuildingPredictiveModels2008}. 

@@

 Table \ref{tab:summary} shows the summary statistics of each variable in its original units. The range of these values shows the level of difference between some vineyards, with operations differing by orders of magnitude in size, yield and average price of sale (See Table \ref{tab:tab1}).

@@

PPCCs values for the transformed, centred and scaled variables are shown in Table \ref{tab:pearson_correlation}. The process of centring and scaling variables changes them so that their mean is centred on 0 and all values are scaled to the variables standard deviation, such that 1 is equal to the variables standard deviation. All correlations were found to be statistically significant (p $<$ 2.200E-16), and except for Average Sale Price all variables were positively correlated. With water use, area harvested and emissions being positively correlated to yield, it can be considered that more resources and area are likely to lead to greater yields. The negative correlations between Average Sale Price and Yield, Water Use, Area and Scope One Emissions each indicated that Area Harvested and Fuel Use separately were not the determining factor for average sale price. The negative correlations are associative, not causal relationships (i.e using more water does not cause lower sale prices).
\par
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \multicolumn{1}{c}{\textbf{Yield}} & \multicolumn{1}{c}{\textbf{Area Harvested}} & \multicolumn{1}{c}{\textbf{Water Used}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}}} & \multicolumn{1}{c}{\textbf{Average Price}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}}} \\ \midrule
          Yield & 1.00 & 0.88 & 0.82 & 0.76 & 0.96 & -0.46 & -0.88 \\
          Area Harvested & 0.88 & 1.00 & 0.78 & 0.83 & 0.73 & -0.19 & -0.81 \\
          Water Used & 0.82 & 0.78 & 1.00 & 0.67 & 0.76 & -0.49 & -0.82 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.76 & 0.83 & 0.67 & 1.00 & 0.65 & -0.16 & -0.67 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.96 & 0.73 & 0.76 & 0.65 & 1.00 & -0.54 & -0.84 \\
          Average Price & -0.46 & -0.19 & -0.49 & -0.16 & -0.54 & 1.00 & 0.72 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.88 & -0.81 & -0.82 & -0.67 & -0.84 & 0.72 & 1.00 \\ \bottomrule
          \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}) and statistical significance of F-tests (p $<$ 2.200E-16). Aside from 3 variables, all regression parameters were also statistically significant from zero, F-tests across each model's variables were (p $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (p=0.22) and Model 4 (p=0.0.39), and the interaction between area harvested and water used in model 2 (p=0.22). Note that scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5) especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). 
%A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 0.9072 & 0.9061 & 775.3 & 2.200e-16 & 0.3065 & 491.3 & 0.1 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 0.8291 & 0.8141 & 55.07 & 2.200e-16 & 0.4312
           & 905.03 & 0.19 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} &0.9753 &0.9748 & 1885 & 2.200e-16 & 0.1589 & 71.11 & 0.03 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 0.9091 & 0.9006 & 106.1 & 2.200e-16 & 0.3153  & 261.41 & 0.10 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

Coefficients related to continuous variables are summarised in Table \ref{tab:contvar}. In Model 1 all coefficients except for the intercept significantly contributed to the model (p $<$ 0.05), and in Model 2 all coefficients were statistically significant (p $<$ 0.05). However, scope one emissions did not significantly contribute to models 3, 4 and 5. Model 4 only had statistically significant contributions from the intercept and water use. Although the coefficient for water use was statistically significant for each model, it did not have the highest value; instead, area harvested, being an order of magnitude greater, dominated the models. Model 5 achieved a similar $R^2$ to Model 4 without area harvested, having stronger influences from water use and scope one emissions.

@@

Although not chosen over GI region, climate was considered to be a large determinant of the ability to produce larger quantities of grapes, as well as a determinant in grape sale price \cite{agostaRegionalClimateVariability2012}. The more granular GI Region likely explained a broader mix of geographical phenomenon, such as soil, geology and access to water resources \cite{abbalDecisionSupportSystem2016,carmonaUseParticipatoryObjectOriented2011}. The interaction between year and GI Region likely accounted for events such as bushfires, which would be impactful, but only at a local level, both in time and space.

>>>>

The focus on sustainability in agronomic industries has changed the way in which these enterprises do business. The diverse nature of vineyard operations results in complicated interactions with both environmental and economic outcomes. The interactions between different factors can put an environmentally advantageous decision at odds with an economic one, and conversely economic decisions can be detrimental to the environment~\cite{beaumelleBiodiversityConservationEcosystem2023}. As a result many studies are including more diverse ranges of data and scales. However, studies tend to focus on specific aspects, such as reducing chemical use or improving soil health, often focusing on singular relationships or variable outcomes~\cite{barriguinhaVineyardYieldEstimation2021,heFruitYieldPrediction2022,laurentReviewIssuesMethods2021}. Other analyses, look at life cycles or cost benefit analyses, reflecting a specific management decision's outcome~\cite{abbottAWRIAssessingEnvironmental2016,beauchetInterannualVariabilityEnvironmental2019,ferraraLifeCycleAssessment2018} or their cost benefits by utilising different scenarios to assess specific practices~\cite{fincoCombiningPrecisionViticulture2022a,singhBibliometricReviewUse2022}. It has been noted that some studies have relied too heavily on single points of engagement when relaying the idea of sustainability and vineyard outcomes, especially when the inclusion of more variables or data could have better described a situation as a whole~\cite{baianoOverviewSustainabilityWine2021,santiago-brownSustainabilityAssessmentWineGrape2015}. The changing nature of sustainability also calls for measures to be more than simple snapshots of data~\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023,santiago-brownSustainabilityAssessmentWineGrape2015}. Given recent studies there is still growing interest from the winegrowing industry in further studies, with several recent reviews calling for more research to demonstrate the potential trade-offs between different operational approaches across different climates and regions~\cite{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.

A dilemma exists across agriculture through shared fundamental considerations of resource use such as water and fuel, and the resultant yield and crop value that are produced~\cite{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. The average price of grapes for wine production is driven through its integration within the wine industry. An important connection between grapes and their price is the grape's perceived quality, which initially defines a wine's potential through the grape's chemical makeup~\cite{blackTerpenoidsTheirRole2015,schreierFlavorCompositionWines1979}. Grapes of higher perceived quality or grapes from well known regions are likely to have higher prices~\cite{wineaustraliaNationalVintageReport2021}.  Grape quality is connected to the market value of winegrapes, with Wine Australia explicitly defining grape quality through the use of discrete price brackets in their annual reports~\cite{winemakersfederationofaustraliaNationalVintageReport2018}. It is important to note that the generalisation made to reflect quality through using average price assumes a due diligence of those who purchase the grapes~\cite{yeggeInfluenceSensoryNonsensory2001}. The economic sustainability of a vineyard is tied to this market culture, driven by the wine industry. The consideration of sustainability within viticulture is also subject to environmental and sociodemographic pressures~\cite{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these pressures include biosecurity, climate and international market changes~\cite{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the varied effects of factors on grape quality and yield~\cite{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. Due to the lack of long-term and in-depth data there is a lack of research on grape sale price and its driving factors. Furthermore, individual factors are often studied in isolation with yield and sales price not appearing together~\cite{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions. As a result, broader studies are lacking~\cite{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and average sale price of the resultant product, taking into account the size and location of the vineyard. In a practical sense, this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the trade-off between invested resources, yield and average sale price. This is the first time that such a trade-off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section*{Methods}
\subsection*{Data}

@@

Data used in these analyses were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape  growers and winemakers in demonstrating and improving their sustainability~\cite{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act~\cite{attorney-generalsdepartmentWineAustraliaCorporation2010}. Data collected by Wine Australia are publicly available. The response (predicted) variables in this analysis were yield, defined as the total tonnes of grapes harvested, and average sale price of grapes in Australian dollars per tonne. Both response variables were examined as totals and also relative to area harvested (see Table~\ref{tab:tab1}). Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

Data recorded by Sustainable Winegrowing Australia were entered manually by winegrowers voluntarily using a web based interface. For each model, vineyards were only included if they recorded all the variables used for the corresponding model (see Table~\ref{tab:tab1}). Each vineyard had at least recorded region, harvest year, yield and area harvested. Other variables that were used but not present for every single vineyard were average sale price, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable direct comparisons between fuels, fuel use was converted to tonnes of carbon dioxide equivalent and collectively referenced to as emissions. All variables were continuous except for harvest year and region, which were categorical variables (Table~\ref{tab:tab1}).

@@

The dataset was split into two distinct subsets that could be used across the different models. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table~\ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for three further models (Models 3, 4 and 5, see Table~\ref{tab:tab1}). These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table~\ref{tab:tab1}), as every sample/vineyard had a recorded value for yield but not average price of sale per tonne.

@@

The first subset of data (used for Model 1 and Model 2, see Table~\ref{tab:tab1}) contained 5298 samples spanning the period from 2012 to 2022, covering 55 GI Regions and 1261 discrete vineyards.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table~\ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards. Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

Data preprocessing was conducted prior to analysis using the Python programming language~\cite{g.vanrossumPythonTutorialTechnical1995}. Preprocessing included the conversion of fuel to scope one emissions and prior calculations for all continuous variables which included logarithmic transformations, centring and scaling by standard deviation. 
We converted multiple emission sources into scope one emissions using the equation given from the Australian National Greenhouse Accounts Factors~\cite{agdeeNationalGreenhouseAccounts2021}. The calculation conducted using

@@

where emissions was the the product of the quantity of fuel in litres, $Q$, a prescribed Energy Content, $EC$, and emission factors (as given by the Australian National Greenhouse Accounts factors) of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide Emission equivalent, $tCO2e$~\cite{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

  % \includegraphics{fig1.pdf}}

@@

Differences in vineyard locations were captured through the use of Geographical Indicator Regions defined by Wine Australia~\cite{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Although vineyards generally differed in income, there were pronounced differences between regions as shown in Figure~\ref{fig:map}. These differences were likely due to the site of a vineyard being important as it predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and average sale price~\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act~\cite{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

 The climatic properties of each GI Region were summarised by using predefined classifications as per the~\cite{sustainablewinegrowingaustraliaSustainableWinegrowingAustralia2021} user manual. The user manual describes climates by rainfall and temperature, creating supersets of Regions of similar climatic properties. The climatic groups were used to illustrate similarities and differences occurring in areas larger than GI Regions.

@@

Five general linear models (GLMs) were created (see Table~\ref{tab:tab1}). GLMs were chosen as they offer the ability to produce statistical models that are explicit in the relationships between predictors and response variables.  General Linear Models also allowed the exploration of interactions between predictors and allow for easily comparable differences in the influence and magnitude of relationships. Model fit was measured in terms of $R^2$ and adjusted $R^2$ as well as F statistics, and t-tests were used to determine if predictors significantly contributed to the models when accounting for other variables, showing which specific years and areas contributed significantly. Both the PPCC and GLM analyses were created using the R statistical programming language~\cite{rcoreteamLanguageEnvironmentStatistical2021} with the Caret package~\cite{kuhnBuildingPredictiveModels2008}. 

@@

 Table~\ref{tab:summary} shows the summary statistics of each variable in its original units. The range of these values shows the level of difference between some vineyards, with operations differing by orders of magnitude in size, yield and average price of sale (See Table~\ref{tab:tab1}).

@@

PPCCs values for the transformed, centred and scaled variables are shown in Table~\ref{tab:pearson_correlation}. The process of centring and scaling variables changes them so that their mean is centred on 0 and all values are scaled to the variables standard deviation, such that 1 is equal to the variables standard deviation. All correlations were found to be statistically significant (p $<$ 2.200E-16), and except for Average Sale Price all variables were positively correlated. With water use, area harvested and emissions being positively correlated to yield, it can be considered that more resources and area are likely to lead to greater yields. The negative correlations between Average Sale Price and Yield, Water Use, Area and Scope One Emissions each indicated that Area Harvested and Fuel Use separately were not the determining factor for average sale price. The negative correlations are associative, not causal relationships (i.e using more water does not cause lower sale prices).
\par
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \multicolumn{1}{c}{\textbf{Yield}} & \multicolumn{1}{c}{\textbf{Area Harvested}} & \multicolumn{1}{c}{\textbf{Water Used}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}}} & \multicolumn{1}{c}{\textbf{Average Price}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}}} \\ \midrule
          Yield & 1.00 & 0.88 & 0.82 & 0.76 & 0.96 & -0.46 & -0.88 \\
          Area Harvested & 0.88 & 1.00 & 0.78 & 0.83 & 0.73 & -0.19 & -0.81 \\
          Water Used & 0.82 & 0.78 & 1.00 & 0.67 & 0.76 & -0.49 & -0.82 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.76 & 0.83 & 0.67 & 1.00 & 0.65 & -0.16 & -0.67 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.96 & 0.73 & 0.76 & 0.65 & 1.00 & -0.54 & -0.84 \\
          Average Price & -0.46 & -0.19 & -0.49 & -0.16 & -0.54 & 1.00 & 0.72 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.88 & -0.81 & -0.82 & -0.67 & -0.84 & 0.72 & 1.00 \\ \bottomrule
          \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}) and statistical significance of F-tests (p $<$ 2.200E-16). Aside from 3 variables, all regression parameters were also statistically significant from zero, F-tests across each model's variables were (p $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (p=0.22) and Model 4 (p=0.0.39), and the interaction between area harvested and water used in model 2 (p=0.22). Note that scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5) especially for Models 1 and 4 (Table~\ref{tab:pearson_correlation}). 
%A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 0.9072 & 0.9061 & 775.3 & 2.200e-16 & 0.3065 & 491.3 & 0.1 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 0.8291 & 0.8141 & 55.07 & 2.200e-16 & 0.4312
           & 905.03 & 0.19 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} &0.9753 &0.9748 & 1885 & 2.200e-16 & 0.1589 & 71.11 & 0.03 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 0.9091 & 0.9006 & 106.1 & 2.200e-16 & 0.3153  & 261.41 & 0.10 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

Coefficients related to continuous variables are summarised in Table~\ref{tab:contvar}. In Model 1 all coefficients except for the intercept significantly contributed to the model (p $<$ 0.05), and in Model 2 all coefficients were statistically significant (p $<$ 0.05). However, scope one emissions did not significantly contribute to models 3, 4 and 5. Model 4 only had statistically significant contributions from the intercept and water use. Although the coefficient for water use was statistically significant for each model, it did not have the highest value; instead, area harvested, being an order of magnitude greater, dominated the models. Model 5 achieved a similar $R^2$ to Model 4 without area harvested, having stronger influences from water use and scope one emissions.

@@

Although not chosen over GI region, climate was considered to be a large determinant of the ability to produce larger quantities of grapes, as well as a determinant in grape sale price~\cite{agostaRegionalClimateVariability2012}. The more granular GI Region likely explained a broader mix of geographical phenomenon, such as soil, geology and access to water resources~\cite{abbalDecisionSupportSystem2016,carmonaUseParticipatoryObjectOriented2011}. The interaction between year and GI Region likely accounted for events such as bushfires, which would be impactful, but only at a local level, both in time and space.
